---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# bettRtab

<!-- badges: start -->
[![Version-Number](https://img.shields.io/github/r-package/v/JaseZiv/bettRtab?label=bettRtab (Dev))](https://github.com/JaseZiv/bettRtab/)
[![R build status](https://github.com/JaseZiv/bettRtab/workflows/R-CMD-check/badge.svg)](https://github.com/JaseZiv/bettRtab/actions)
<!-- badges: end -->

## Overview

This package is designed to allow users to obtain clean and tidy TAB betting markets for both racing and sports. It gives users the ability to access data more efficiently.


## Installation


You can install the released version of [**```bettRtab```**](https://github.com/JaseZiv/bettRtab/) from [GitHub](https://github.com/JaseZiv/bettRtab) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("JaseZiv/bettRtab")
```


## Usage

The functions in this package should work without hitch locally, but running these in an automated way (GitHub Actions, cloud, etc) may lead to requests being blocked.

To get around this, you will need access to proxies and would need to set configs at the start of your scripts similar to the following:

```{r}
httr::set_config(httr::use_proxy(url = Sys.getenv("PROXY_URL"),
                                 port = as.numeric(Sys.getenv("PROXY_PORT")),
                                 username =Sys.getenv("PROXY_USERNAME"),
                                 password= Sys.getenv("PROXY_PASSWORD")))


